FTLR proof cases

### 2018-03-11 fully-abstract-comp/ftlr-proof-cases.tex
Some more work on the FTLR cases.

\begin{definition}[purePart]
  For any world $W$, we define
  \begin{align*}
    \purePart{W} &\defeq (\purePart{\pwheap},\purePart{\pwpriv},\purePart{\pwfree})\\
    \purePart{W_\var{heap}} &\defeq
                       \begin{cases}
                         W_{\var{heap}}(r) & \text{if } W_\var{heap}(r) = (pure,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_\var{heap}(r) = (\spatial,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_\var{heap}(r) = (\spatialo,\var{sm})\\
                         \revoked & \text{if } W_\var{heap}(r) = \revoked\\
                       \end{cases}\\
    \purePart{W_\var{priv}} &\defeq
                       \begin{cases}
                         ((\spatial,\var{sm}),\sigma) & \text{if } W_\var{priv}(r) = ((\spatial,\var{sm}),\sigma)\\
                         ((\spatial,\var{sm}),\sigma) & \text{if } W_\var{priv}(r) = ((\spatialo,\var{sm}),\sigma)\\
                         (\revoked,\sigma) & \text{if } W_\var{priv}(r) = (\revoked,\sigma)\\
                       \end{cases}
    \purePart{W_\var{free}} &\defeq
                       \begin{cases}
                         W_{\var{free}}(r) & \text{if } W_{\var{free}}(r) = (pure,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_{\var{free}}(r) = (\spatial,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_{\var{free}}(r) = (\spatialo,\var{sm})\\
                         \revoked & \text{if } W_{\var{free}}(r) = \revoked\\
                       \end{cases}
  \end{align*}

\end{definition}
\begin{lemma}[purePart is pure]
 For all $W$, we have that $W = W \oplus \purePart{W}$.
\end{lemma}

\begin{lemma}[non-linear words are pure]
  If $\npair{(w_1,w_2)} \in \lrv{W}$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv{\purePart{W}}$.
\end{lemma}

>>>>

\begin{definition}[purePart]
  For any world $W$, we define
  \begin{align*}
    \purePart{W} &\defeq (\purePart{\pwheap},\purePart{\pwpriv},\purePart{\pwfree})\\
    \purePart{W_\var{heap}} &\defeq
                       \begin{cases}
                         W_{\var{heap}}(r) & \text{if } W_\var{heap}(r) = (pure,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_\var{heap}(r) = (\spatial,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_\var{heap}(r) = (\spatialo,\var{sm})\\
                         \revoked & \text{if } W_\var{heap}(r) = \revoked\\
                       \end{cases}\\
    \purePart{W_\var{priv}} &\defeq
                       \begin{cases}
                         ((\spatial,\var{sm}),\sigma) & \text{if } W_\var{priv}(r) = ((\spatial,\var{sm}),\sigma)\\
                         ((\spatial,\var{sm}),\sigma) & \text{if } W_\var{priv}(r) = ((\spatialo,\var{sm}),\sigma)\\
                         (\revoked,\sigma) & \text{if } W_\var{priv}(r) = (\revoked,\sigma)\\
                       \end{cases}\\
    \purePart{W_\var{free}} &\defeq
                       \begin{cases}
                         W_{\var{free}}(r) & \text{if } W_{\var{free}}(r) = (pure,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_{\var{free}}(r) = (\spatial,\var{sm})\\
                         (\spatial,\var{sm}) & \text{if } W_{\var{free}}(r) = (\spatialo,\var{sm})\\
                         \revoked & \text{if } W_{\var{free}}(r) = \revoked\\
                       \end{cases}
  \end{align*}
\end{definition}

\begin{lemma}[purePart is pure]
 For all $W$, we have that $W = W \oplus \purePart{W}$.
\end{lemma}

\begin{lemma}
  \label{lem:world-fut-purePart}
  For all $W$, we have that $W \future \purePart{W}$.
  \dominique{11-3-2018: Err.. this doesn't seem to hold as we don't have that $\spatialo \future \spatial$. This also means that we don't currently have that $W_1 \oplus W_2 \future W_1$. Shouldn't we?  }
\end{lemma}

\begin{lemma}[non-linear words are pure]
  If $\npair{(w_1,w_2)} \in \lrv(H_\sigma,W)$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv(H_\sigma,\purePart{W})$.
  \dominique{11-3-2018: proving this lemma depends on lemma~\ref{lem:world-fut-purePart} for the higher-order cases.}
\end{lemma}
